Constructing the transition graphs of interacting hysterons

### 2022-06-03 Paper_draft.tex
Added comment on base/relaxation ineqs to piece on avalanches

 We see that every transition $S^{(0)}\rightarrow S^{(1)}$ in the base graph can be extended to a $l=2$ transition  $S^{(0)}\rightarrow S^{(1)}\rightarrow S^{(2)}$ in at most two ways. However, not every avalanche is necessarily valid. This is because an avalanche may not contain any cycles: if an avalanche did contain a cycle, it would lead to an infinite loop. We must therefore impose that $S^{(2)} \neq S^{(0)}$. As a result, the number of avalanche options per transition is either two, one, or zero.\\

\section{Application to specific models}
We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear. Linear coupling entails that the switching fields $U_i^{+, -}(S)$ depend on the state $S$ as:
\begin{equation}
    U_i^{+, -}(S) = u_i^{+, -} -\sum_{i \neq j}c_{ij}s_j
\end{equation}
Depending on the system, the allowed coupling coefficients $c_{ij}$ may be restricted. We consider two instances of the linear model for $N=3$. First, we look at the case where only one of the coupling coefficients $c_{ij}$ is unequal to zero. Second, we look at a model for hysterons in series, where the coupling is $c_{ij}  = c_j$ with all $c_j < 0$.\\
\subsection{Linear coupling}
%\begin{figure}[!ht]
%    \centering
%    \includegraphics[width=0.5\textwidth]{.png}
%    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
%    \label{fig:linear_coupling}
%\end{figure}\\
\subsection{Hysterons in series}
\section{Discussion}
\section{Outlook}
%\bibliography{apssamp}% Produces the bibliography via BibTeX.

>>>>

 We see that every transition $S^{(0)}\rightarrow S^{(1)}$ in the base graph can be extended to a $l=2$ transition  $S^{(0)}\rightarrow S^{(1)}\rightarrow S^{(2)}$ in at most two ways, by choosing either $S^{(2)} = S^{(2+)}$ or $S^{(2)} = S^{(2-)}$ . However, not every avalanche is necessarily valid. This is because an avalanche may not contain any cycles: if an avalanche did contain a cycle, it would lead to an infinite loop. We must therefore impose that $S^{(2)} \neq S^{(0)}$. As a result, the number of avalanche options per transition is either two, one, or zero.\\
By extending one of the transitions ina  graph from length $l=1$ to length $l=2$, we modify its design inequalities (see SI). In particular, we change the relaxation inequalities that describe the stability of the state $S^{(1)}$. We also add a new set of relaxation inequalities so that the state $S^{(2)}$ is stable.\\
\section{Application to specific models}
We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear. Linear coupling entails that the switching fields $U_i^{+, -}(S)$ depend on the state $S$ as:
    U_i^{+, -}(S) = u_i^{+, -} -\sum_{i \neq j}c_{ij}s_j
Depending on the system, the allowed coupling coefficients $c_{ij}$ may be restricted. We consider two instances of the linear model for $N=3$. First, we look at the case where only one of the coupling coefficients $c_{ij}$ is unequal to zero. Second, we look at a model for hysterons in series, where the coupling is $c_{ij}  = c_j$ with all $c_j < 0$.\\
\subsection{Linear coupling}
%\begin{figure}[!ht]
%    \centering
%    \includegraphics[width=0.5\textwidth]{.png}
%    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
%    \label{fig:linear_coupling}
%\end{figure}\\
\subsection{Hysterons in series}
\section{Discussion}
\section{Outlook}
%\bibliography{apssamp}% Produces the bibliography via BibTeX.
